\section{Conclusion}
%Resumir que proponemos
We have proposed a distributed model to store historic transaction 
records about vehicles ownership through blockchain technology.
We believe our proposal may contribute to extend the paperless culture.
At the same time, it will help solve some loopholes on vehicle purchase transactions
that can be exploited to commit a fraud. 

Even though our model presents the transaction logic 
followed specifically on some Latin American countries, 
it can be applied to other countries around the world 
who are looking to have a digital ecosystem 
that have better control over the transaction history a vehicle can have 
throughout its life cycle.

%Cuáles son los alcances de lo que proponemos
The model involves the creation of a genesis block by a vehicle manufacturer,
the blockchain operation of different distributed transactions including, selling,
change of legal status, add important information, etc. 
This information might be poured on a system 
where services will be available for quick access, ie. theft and debt status, 
different owners, etc.

We have included the description of all participants and how they interact in terms of 
messages. 
We take care of security aspects in the exchange of messages 
detailing all the TLS protocol and how it is connected with the transactions of the blockchain.

%Decir quién es nuestro universo de nuestra contribución
We believe that the proposed model can be interesting for owners, government, insurance companies, 
vehicle purchase companies or dealerships. 
Owners always will be grateful for having better and faster solutions for services. 
Government could give more and better services granting accuracy, transparency in the transactions, 
speed in procedures (without need to process documents manually), all while being paper free. 
Insurance companies could have a better estimation about the price of vehicles. 
Vehicle purchase companies benefit also when they acts as owners of multiple vehicles.

%Our proposal is ongoing work, this will continue in:
%\begin{itemize}
%    \item Specify in detail those functions that are part of the smart property.
%    \item Perform the earnings mechanism as done by Ethereum or Bitcoin; and
%    \item Develop a prototype: client application with a wallet-vehicle and the
%        server side, specifying if all blockchain infrastructure is implemented on 
%        Ethereum or create our own blockchain network.
%\end{itemize} 